---
title: "The Kitchen Sink"
author: "Chip Oglesby"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output:
  github_document:
   html_preview: FALSE
pdf_document:
  toc: false
---


## What are the most mentioned restaurants?
```{r one, echo = FALSE, warning = FALSE, message = FALSE}
favoriteResturants %>% 
  knitr::kable()
```

## Who talks about sherry?
```{r two, echo = FALSE, warning = FALSE, message = FALSE}
sherryReferences %>% 
  knitr::kable()
```

## Who talks about coffee?
```{r three, echo = FALSE, warning = FALSE, message = FALSE}
coffeeReferences %>% 
  knitr::kable()
```


## Who talks about Eddie??
```{r four, echo = FALSE, warning = FALSE, message = FALSE}
eddieReferences %>% 
  knitr::kable()
```


## Who talks about beer?
```{r five, echo = FALSE, warning = FALSE, message = FALSE}
beerReferences %>% 
  knitr::kable()
```

## Who talks about Opera?
```{r six, echo = FALSE, warning = FALSE, message = FALSE}
operaReferences %>% 
  knitr::kable()
```

## Who talks about Roz?
```{r seven, echo = FALSE, warning = FALSE, message = FALSE}
rozReferences %>% 
  knitr::kable()
```

## Who talks about Daphne?
```{r eight, echo = FALSE, warning = FALSE, message = FALSE}
daphneReferences %>% 
  knitr::kable()
```

## Who talks about Maris?
```{r nine, echo = FALSE, warning = FALSE, message = FALSE}
marisReferences %>% 
  knitr::kable()
```

## Who talks about Lilith?
```{r ten, echo = FALSE, warning = FALSE, message = FALSE}
lilithReferences %>% 
  knitr::kable()
```

## Which brother introduces themselves as doctor?
```{r eleven, echo = FALSE, warning = FALSE, message = FALSE}
drReferences %>% 
  knitr::kable()
```

## Who talks about mom the most?
```{r tweleve, echo = FALSE, warning = FALSE, message = FALSE}
momReferences %>% 
  knitr::kable()
```

## How many times does frasier say hello seattle or I'm listening?
```{r thirteen, echo = FALSE, warning = FALSE, message = FALSE}
listeningReferences %>% 
  knitr::kable()
```

## Is Frasier the only one who says DEAR GOD
```{r fourteen, echo = FALSE, warning = FALSE, message = FALSE}
godReferences %>% 
  knitr::kable()
```